---
title: "`r params$iraise`"
author: "Damian Villagra"
date: "`r format(Sys.Date(), '%d/%m/%Y')`"
output:
  html_document:
    toc: true
    toc_depth: 5
    toc_float: true
    theme: readable
    code_folding: hide
    df_print: paged
    self_contained: true
params:
  istock: NULL
  iraise: NULL
  stock_inputs: NULL
  stock_outputs: NULL
  stock_tables: NULL
editor_options: 
  chunk_output_type: console
---
```{r setup, include=FALSE}
#
# params <- list(
#   istock = istock,
#   iraise = iraise,
#   stock_inputs  = all_inputs[[iraise]],
#   stock_outputs = all_outputs[[iraise]],
#   stock_tables  = all_tables[[iraise]]
# )

# --- Load named lists into global environment ---
inputs  <- params$stock_inputs
outputs <- params$stock_outputs
tables  <- params$stock_tables
meta    <- params$stock_inputs$metadata
istock <- params$istock
iraise <- params$iraise

# Example: create a stock title safely
istock_title <- paste(
iraise
)

ncol_val_lan <- ifelse(toupper(meta$iYQ$Lan) == "YEAR", 1, 2)
fig_height_lan <- ifelse(toupper(meta$iYQ$Lan) == "YEAR", 10, 20)
fig_width_lan <- ifelse(toupper(meta$iYQ$Lan) == "YEAR", 15, 15)

ncol_val_dis <- ifelse(toupper(meta$iYQ$Dis) == "YEAR", 1, 2)
fig_height_dis <- ifelse(toupper(meta$iYQ$Dis) == "YEAR", 10, 20)
fig_width_dis <- ifelse(toupper(meta$iYQ$Dis) == "YEAR", 15, 15)


# Define logical flags with hierarchical dependency
has_weights <- meta$iRaisingLevel %in% c("WEIGHTS", "LENGTHS", "LWK", "AGE", "ALL")
has_lengths <- meta$iRaisingLevel %in% c("LENGTHS", "LWK", "AGE", "ALL")
has_LWK     <- meta$iRaisingLevel %in% c("LWK", "AGE", "ALL")
has_ALK     <- meta$iRaisingLevel %in% c("AGE", "ALL")
has_all     <- meta$iRaisingLevel %in% c("ALL")

# Optional: more granular flags for specific cases
has_weights_only <- meta$iRaisingLevel == "WEIGHTS"
has_lengths_only <- meta$iRaisingLevel == "LENGTHS"
```

```{r loading libraries, echo = FALSE,message = FALSE,warning = F}
# knitr::opts_chunk$set(echo = TRUE)
library(RODBC)
library(tidyr)
library(dplyr)
library(zoo)
library(FSA)
library(nnet)
library(ggplot2)
library(data.table)
library(gdata)
library(httr)
library(XML)
library(readxl)
library(stringr)
library(mapplots)
library(mapdata)
library(smartfish)
library(ndgp.ices.rdbexchfmt)
library(DT)
library(ggpubr)
library(kableExtra)
library(cowplot)
library(DT)
library(dplyr)
library(knitr)
```

# 1. Summary data

```{r metadata_stock_summary, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
# --- Helper for raised summary ---
get_raised_summary <- function(level) {
  parts <- c()
  if (level %in% c("WEIGHTS", "LENGTHS", "LWK", "AGE", "ALL")) parts <- c(parts, "Weights")
  if (level %in% c("LENGTHS", "LWK", "AGE", "ALL")) parts <- c(parts, "Lengths")
  if (level %in% c("LWK", "AGE", "ALL")) parts <- c(parts, "LWK")
  if (level %in% c("AGE", "ALL")) parts <- c(parts, "ALK")
  if (length(parts) == 0) "No raised data available" else paste(parts, collapse = " + ")
}

# --- Build rows as a list of named vectors ---
rows <- list(
  c("Stock code",             istock,                    istock),
  c("Species (scientific name)", meta$ispecies,               meta$ispecies),
  c("FAO code",               meta$iFAO,                      meta$iFAO),
  c("AphiaID",                meta$iAphiaID,                  meta$iAphiaID),
  c("Working group (code)",   meta$iWG,                       meta$iWG),
  c("Working group (name)",   meta$iWG_nice,                  meta$iWG_nice),
  c("Metier",                 meta$imet,                      meta$imet),
  c("Year",                   meta$iyear,                     meta$iyear),
  c("Temporal level of raising",                meta$iYQ$Lan,                       meta$iYQ$Dis),
  c("Quantitative level of raising",        meta$iRaisingLevel$Lan,         meta$iRaisingLevel$Dis),
  c("Available raised data",  get_raised_summary(meta$iRaisingLevel$Lan), get_raised_summary(meta$iRaisingLevel$Dis)),
  c("LWK method",
    if (meta$iRaisingLevel$Lan %in% c("LWK", "AGE", "ALL")) meta$iLWK$Lan else "Not performed",
    if (meta$iRaisingLevel$Dis %in% c("LWK", "AGE", "ALL")) meta$iLWK$Dis else "Not performed"
  ),
  c("LWK source",
    if (meta$iRaisingLevel$Lan %in% c("LWK", "AGE", "ALL"))
      if (!is.null(meta$iLWK$Lan) && meta$iLWK$Lan == "calc") "Commercial sampling" else meta$iLWK_source$Lan else "",
    if (meta$iRaisingLevel$Dis %in% c("LWK", "AGE", "ALL"))
      if (!is.null(meta$iLWK$Dis) && meta$iLWK$Dis == "calc") "Commercial sampling" else meta$iLWK_source$Dis else ""
  ),
  c("Areas", paste(meta$iareas, collapse = "; "), paste(meta$iareas, collapse = "; "))
)

# --- Convert to clean data frame ---
metadata_df <- do.call(rbind.data.frame, rows)
names(metadata_df) <- c("Parameter", "Lan", "Dis")
metadata_df[] <- lapply(metadata_df, as.character)

# --- Display in datatable ---
DT::datatable(
  metadata_df,
  escape = FALSE,
  caption = "Table 0. Summary of raising metadata",
  options = list(
    dom = 't',
    paging = FALSE,
    autoWidth = TRUE
  ),
  rownames = FALSE
)

skip_following <- (meta$iRaisingLevel$Lan == "XX" && meta$iRaisingLevel$Dis == "XX")
```

# 2. Summary of input data available for the stock

```{r tables_stock_summary, echo=FALSE, warning=FALSE, message=FALSE, results='asis', eval = !skip_following}

library(dplyr)
library(tidyr)

# Add a column identifying the dataset
Trips_labeled <- lapply(names(inputs$Trips), function(ds) {
  df <- inputs$Trips[[ds]]
  if(nrow(df) == 0) return(df)  # skip empty
  df %>% mutate(Dataset = ds)
})

# Combine all trips into a single long data frame
all_trips_long <- plyr::rbind.fill(Trips_labeled)

# Spread into a wide table: one row per Trip+Quarter, columns = datasets
trips_wide <- all_trips_long %>%
  mutate(Present = "X") %>%
  pivot_wider(
    id_cols = c(Trip, Quarter),
    names_from = Dataset,
    values_from = Present,
    values_fill = ""
  ) %>%
  arrange(Trip, Quarter)

# Display
DT::datatable(
  trips_wide,
  rownames = FALSE,
   filter = "top",
  caption = "Trips presence across datasets with Quarter info",
  options = list(
    pageLength = 20,
    autoWidth = TRUE
  )
)

number_summary <- full_join(
    full_join(inputs$NumLength, inputs$NumWeight, by = c("SAcatchCat","Quarter")),
    inputs$NumAge, by = c("SAcatchCat","Quarter")
  ) %>%
  arrange(SAcatchCat, Quarter) %>%        # sort by SAcatchCat and Quarter
  relocate(SAcatchCat, Quarter)   

# Rename catch category column
colnames(number_summary) <- c("Catch category", "Quarter", "Number of lengths","Number of weights","Number of ages")

# Display as datatable
DT::datatable(
  number_summary,
  rownames = FALSE,
  caption = "Table: Total number at length and age by catch category",
  options = list(pageLength = 10, autoWidth = F)
)
```

# 3. Summary of raised output

## 3.1 Raised total weights 

### 3.1.1 domainCatchDis in catch table (CN)

```{r domainCatchDis, echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=15, fig.height=10}
library(dplyr)
library(DT)

# Get all non-empty domainCatchDis entries
domainCatchDis <- tables$catch %>%
  dplyr::filter(domainCatchDis != "") %>%
  dplyr::distinct(domainCatchDis, catchCategory, seasonValue, areaValue, metier6)

# Build a domain "key" stripping the catchCategory suffix to match Lan <-> Dis pairs
# Assumes domainCatchDis ends in _Lan or _Dis
domainCatchDis <- domainCatchDis %>%
  dplyr::mutate(
    domain_base = stringr::str_remove(domainCatchDis, "_(Lan|Dis)$")
  )

# Check Lan/Dis pairing per base domain + season + area + metier
domain_pairs <- domainCatchDis %>%
  dplyr::group_by(domain_base) %>%
  dplyr::summarise(
    has_Lan = any(catchCategory == "Lan"),
    has_Dis = any(catchCategory == "Dis"),
    .groups  = "drop"
  ) %>%
  dplyr::mutate(
    status = dplyr::case_when(
      has_Lan & has_Dis   ~ "OK",
      has_Lan & !has_Dis  ~ "⚠️ Landings domain present but Discards missing",
      !has_Lan & has_Dis  ~ "⚠️ Discards domain present but Landings missing",
      TRUE                ~ "Unknown"
    )
  ) %>%
  dplyr::arrange(status, domain_base)

# Render
datatable(
  domain_pairs,
  caption  = paste0("Summary of domainCatchDis in catch table (CN) - ", istock),
  options  = list(pageLength = 20, autoWidth = TRUE),
  rownames = FALSE
) %>%
  DT::formatStyle(
    "status",
    backgroundColor = DT::styleEqual(
      c("OK",
        "⚠️ Landings domain present but Discards missing",
        "ℹ️ Discards domain present but Landings missing"),
      c("#d4edda", "#f8d7da", "#fff3cd")
    )
  )
```

### 3.1.2. Landings and discards raised weights 

```{r RW_table_plot, echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=15, fig.height=10}
library(dplyr)
library(DT)
library(ggplot2)

# Round and prepare RW table for display
RW_table <- outputs$RW %>%
  mutate(
    DR = round(DR, 2),
    LW = round(LW, 3),
    DW = round(DW, 3),
    DW_Var = round(DW_Var, 1),
    DW_SD = round(DW_SD, 1),
    CI_low = round(CI_low, 1),
    CI_high = round(CI_high, 1),
    Quarter = as.character(Quarter)
  ) %>%
  dplyr::select(Quarter, DR, LW, DW, DW_Var, DW_SD, CI_low, CI_high)

# Optionally pivot longer for nicer table display
# RW_table_long <- RW_table %>%
  # tidyr::pivot_longer(cols = -Quarter, names_to = "Parameter", values_to = "Value")

# Render interactive datatable
datatable(
  RW_table,
  caption = paste0("Summary of Raised Catch (RW) - ", istock),
  options = list(pageLength = 20, autoWidth = TRUE),
  rownames = FALSE
)

library(dplyr)
library(tidyr)
library(ggplot2)

# --- Prepare data ---
RW_plot_df <- outputs$RW %>%
  mutate(
    Quarter = factor(Quarter, levels = sort(unique(Quarter))),
    Landings = LW,
    Discards = DW,
    LowerCI = CI_low,
    UpperCI = CI_high,
    DR_percent = round(DR * 100, 1),
    DR_real = Discards / (Discards+Landings) *100
  ) %>%
  pivot_longer(
    cols = c("Landings", "Discards"),
    names_to = "Category",
    values_to = "Weight"
  ) %>%
  mutate(
    LowerCI = ifelse(Category == "Discards", LowerCI, NA),
    UpperCI = ifelse(Category == "Discards", UpperCI, NA)
  )

label_df <- RW_plot_df %>%
  mutate(
    Weight_t = Weight / 1000,
    LowerCI_t = LowerCI / 1000,
    UpperCI_t = UpperCI / 1000,
    label_text = ifelse(
      Category == "Discards" & !is.na(LowerCI),
      paste0(
        sprintf("%.1f", Weight_t), " t (",
        sprintf("%.1f", LowerCI_t), " – ",
        sprintf("%.1f", UpperCI_t), " t)"
      ),
      paste0(sprintf("%.1f", Weight_t), " t")
    ),
    # Compute y position per row, accounting for error bar height on Discards
    y_label = ifelse(
      Category == "Discards" & !is.na(UpperCI),
      UpperCI_t + max(RW_plot_df$Weight / 1000, na.rm = TRUE) * 0.03,
      Weight_t  + max(RW_plot_df$Weight / 1000, na.rm = TRUE) * 0.03
    )
  )

# --- Create DR% text data ---
dr_label_df <- RW_plot_df %>%
  filter(Category == "Landings") %>%
  distinct(Quarter, DR_percent, DR_real) %>%
  mutate(
    y_pos       = max(RW_plot_df$Weight, na.rm = TRUE) / 1000 * 1.15,
    y_pos_real  = max(RW_plot_df$Weight, na.rm = TRUE) / 1000 * 1.08,
    label       = paste0("DW/LW: ", DR_percent, "%"),
    label_real  = paste0("DR: ", round(DR_real, 1), "%")
  )

# --- Plot ---
ggplot(RW_plot_df, aes(x = Quarter, y = Weight / 1000, fill = Category)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.8),
           width = 0.7, color = "black") +
  geom_errorbar(aes(ymin = LowerCI / 1000, ymax = UpperCI / 1000),
                position = position_dodge(width = 0.8),
                width = 0.2, color = "black") +
  geom_text(
    data = dr_label_df,
    aes(x = Quarter, y = y_pos, label = label),
    inherit.aes = FALSE,
    vjust = 0, size = 4, fontface = "bold"
  ) +
  geom_text(
    data = dr_label_df,
    aes(x = Quarter, y = y_pos_real, label = label_real),
    inherit.aes = FALSE,
    vjust = 0, size = 3.5, fontface = "italic", color = "grey30"
  )  +
 geom_text(
    data = label_df,
    aes(x=Quarter,
      label = label_text,
      y = Weight / 1000 + max(RW_plot_df$Weight / 1000, na.rm = T) * 0.03,
      group = Category
    ),
    position = position_dodge(width = 0.8),
    size = 4,
    vjust = 0, inherit.aes = F
  )  +
  labs(
    title = paste0("Raised Catch - ", istock),
    y     = "Weight (tonnes)",
    x     = "Quarter"
  ) +
  theme_bw() +
  scale_fill_manual(values = c("Discards" = "tomato", "Landings" = "steelblue")) +
  theme(legend.position = "top")

```


## 3.2. Length weight key 

### 3.2.1. LWK construction {.tabset}

```{r LWK_summary_plots, echo=FALSE, warning=FALSE, message=FALSE, results='asis', eval=any(has_LWK)}
library(DT)
library(dplyr)
library(gridExtra)
library(ggplot2)

# --- Helper to extract LWK summary ---
prepare_LWK_summary <- function(LWK_obj, cat_name) {
  if (is.null(LWK_obj)) return(NULL)
  if (is.list(LWK_obj) && all(grepl("^Q", names(LWK_obj)))) {
    bind_rows(lapply(names(LWK_obj), function(q) {
      lwk <- LWK_obj[[q]]
      data.frame(
        Quarter = q,
        Category = cat_name,
        Intercept_a = round(lwk$a, 7),
        Slope_b = round(lwk$b, 3),
        NumObservations = nrow(lwk$raw),
        stringsAsFactors = FALSE
      )
    }))
  } else {
    data.frame(
      Quarter = "Year",
      Category = cat_name,
      Intercept_a = round(LWK_obj$a, 7),
      Slope_b = round(LWK_obj$b, 3),
      NumObservations = nrow(LWK_obj$raw),
      stringsAsFactors = FALSE
    )
  }
}

# --- Helper to get plots ---
get_LWK_plots <- function(LWK_obj, cat_name) {
  if (is.null(LWK_obj)) return(NULL)
  if (is.list(LWK_obj) && all(grepl("^Q", names(LWK_obj)))) {
    lapply(names(LWK_obj), function(q) {
      LWK_obj[[q]]$plot + ggtitle(paste(cat_name, q))
    })
  } else {
    list(LWK_obj$plot + ggtitle(cat_name))
  }
}

# --- Determine which categories have LWK ---
plots_list <- list()
summary_list <- list()

if (has_LWK[1]) {
  summary_list[["Lan"]] <- prepare_LWK_summary(outputs$LWK_L, "Lan")
  plots_list[["Lan"]] <- get_LWK_plots(outputs$LWK_L, "Lan")
  outputs$LWK_L <- NULL
}

if (has_LWK[2]) {
  summary_list[["Dis"]] <- prepare_LWK_summary(outputs$LWK_D, "Dis")
  plots_list[["Dis"]] <- get_LWK_plots(outputs$LWK_D, "Dis")
  outputs$LWK_D <- NULL
}

# --- Render tables ---
# Bind all available LWK summaries into one table
if (length(summary_list) > 0) {
  combined_summary <- bind_rows(summary_list, .id = "Category")
  
  # Render single datatable
  datatable(
    combined_summary,
    caption = "Table: LWK model parameters and number of observations for Lan and Dis",
    options = list(pageLength = 10, autoWidth = TRUE),
    rownames = FALSE
  )
}
```

#### 3.2.1.1. Landings

```{r LWK_summary_plots_lan, echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=fig_width_lan, fig.height=fig_height_lan, eval=has_LWK[1]}
if (!is.null(plots_list[["Lan"]])) {

  tmpfile <- tempfile(fileext = ".png")

  png(tmpfile, width = fig_width_lan*100, height = fig_height_lan*100, res = 150)

  lan_combined <- do.call(ggpubr::ggarrange, c(plots_list[["Lan"]]))

  print(lan_combined)   # MUST BE INSIDE PNG DEVICE

  dev.off()             # close only the PNG device

  knitr::include_graphics(tmpfile)
}

# plots_list[["Lan"]] <- NULL

```

#### 3.2.1.2. Discards

```{r LWK_summary_plots_Dis, echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=fig_width_dis, fig.height=fig_height_dis, eval=has_LWK[2]}
if (!is.null(plots_list[["Dis"]])) {

  tmpfile <- tempfile(fileext = ".png")

  png(tmpfile, width = fig_width_dis*100, height = fig_height_dis*100, res = 150)

  dis_combined <- do.call(ggpubr::ggarrange, c(plots_list[["Dis"]]))

  print(dis_combined)   # MUST BE INSIDE PNG DEVICE

  dev.off()             # close only the PNG device

  knitr::include_graphics(tmpfile)
}

# plots_list[["Dis"]] <- NULL

```


## 3.3. Raised numbers at length and mean weight at length {.tabset}

### 3.3.1 domainBiology in catch and length distribution tables (CN and DN)

```{r domainBiology, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
library(dplyr)
library(DT)

# Extract unique domainBiology from catch
domain_catch <- tables$catch %>%
  dplyr::filter(domainBiology != "") %>%
  dplyr::distinct(domainBiology, catchCategory, seasonValue, metier6) %>%
  dplyr::mutate(in_catch = TRUE)

# Extract distribution presence per variableType, then pivot wide
domain_dist <- tables$distribution %>%
  dplyr::filter(domainBiology != "") %>%
  dplyr::filter(distributionType == "LengthTotal") %>%
  dplyr::distinct(domainBiology, catchCategory, variableType) %>%
  dplyr::mutate(present = TRUE) %>%
  tidyr::pivot_wider(
    names_from  = variableType,
    values_from = present,
    names_prefix = "in_distribution_",
    values_fill  = FALSE
  )

# Join
domain_summary <- domain_catch %>%
  dplyr::full_join(domain_dist, by = c("domainBiology", "catchCategory")) %>%
  dplyr::mutate(
    in_catch = tidyr::replace_na(in_catch, FALSE),
    # Replace NA with FALSE for all in_distribution_* columns
    dplyr::across(dplyr::starts_with("in_distribution_"), ~ tidyr::replace_na(.x, FALSE))
  ) %>%
  # Overall status: OK only if catch present AND all distribution types present
  dplyr::mutate(
    status = dplyr::case_when(
      !in_catch                                          ~ "⚠️ Missing in catch",
      in_catch & dplyr::if_all(
        dplyr::starts_with("in_distribution_"), ~ .x)   ~ "OK",
      in_catch & dplyr::if_any(
        dplyr::starts_with("in_distribution_"), ~ .x)   ~ "⚠️ Partially missing in distribution",
      in_catch                                           ~ "⚠️ Missing in distribution",
      TRUE                                               ~ "Unknown"
    )
  ) %>%
  dplyr::arrange(status, domainBiology)

# Render
datatable(
  domain_summary,
  caption  = paste0("Summary of domainBiology in catch and distribution table (CN) for lengths - ", istock),
  options  = list(pageLength = 30, autoWidth = TRUE),
  rownames = FALSE
) %>%
  DT::formatStyle(
    "status",
    backgroundColor = DT::styleEqual(
      c("OK",
        "⚠️ Partially missing in distribution",
        "⚠️ Missing in distribution",
        "⚠️ Missing in catch"),
      c("#d4edda", "#fff3cd", "#f8d7da", "#f8d7da")
    )
  ) %>%
  # Highlight individual in_distribution_* columns: green TRUE, red FALSE
  DT::formatStyle(
    columns = names(domain_summary)[startsWith(names(domain_summary), "in_distribution_")],
    backgroundColor = DT::styleEqual(c(TRUE, FALSE), c("#d4edda", "#f8d7da"))
  )
```

### 3.3.2. Summary table at length {.tabset}

#### 3.3.2.1. Landings

```{r Numbers at length no weight Landings, echo=FALSE, warning=FALSE, message=FALSE, results='asis', eval = has_lengths[1]  & !has_LWK[1]}

# ---- SOP_L summary table ----
LF_summary_L <- outputs$LF %>% filter (SAcatchCat == "Lan"  ) %>% 
  dplyr::select(Quarter, FMclassMeasured,  number_raw_LFD, lenNumfleet) %>%
  mutate(
    lenNumfleet = round(lenNumfleet, 3),
  ) %>%
  rename(
    "Length" = FMclassMeasured,
    "Number_Raw_LFD" = number_raw_LFD,
    "Raised number (no SOP corr) (1000)" = lenNumfleet,
    "Quarter" = Quarter
  )

datatable(
  LF_summary_L,
  caption = htmltools::tags$caption(
    style = 'caption-side: top; text-align: left; color: black; font-weight: bold;',
    paste(
      "Table: Number of fish sampled for length frequency distribution (LFD), raw fleet numbers (no SOP correction) per Year/Quarter"
    )
  ),
  options = list(pageLength = 30, autoWidth = TRUE),
  rownames = FALSE, filter = "top"
)
```

```{r Numbers at length Landings, echo=FALSE, warning=FALSE, message=FALSE, results='asis', eval = has_LWK[1]}
# Function to generate tables for Landings and Discards
# SOP_L summary table
library(dplyr)
library(DT)
library(htmltools)

# ---- SOP_L summary table ----
LWK_summary_L <- outputs$SOP_L$MWAL %>%
  dplyr::select(Quarter, length, number_raw_LFD, number_raw_LWK, number, corr_numbers, indW2, CI_low, CI_high, indW2_var) %>%
    mutate(
    across(c(number, corr_numbers), ~ round(.x, 3)),
    across(c(indW2, CI_low, CI_high, indW2_var), ~ round(.x, 2))
  ) %>%
  rename(
    "Length" = length,
    "Number_Raw_LFD" = number_raw_LFD,
    "Number_Raw_LWK" = number_raw_LWK,
    "Number (1000)" = number,
    "Corrected_Number (1000)" = corr_numbers,
    "Individual_Weight (g)" = indW2,
    "Individual_Weight_CI_Low (g)" = CI_low,
    "Individual_Weight_CI_High (g)" = CI_high,
    "Individual_Variance (g^2)" = indW2_var,
    "Quarter" = Quarter
  )

datatable(
  LWK_summary_L,
  caption = htmltools::tags$caption(
    style = 'caption-side: top; text-align: left; color: black; font-weight: bold;',
    paste(
      "Table: Number of fish sampled for length frequency distribution (LFD),",
      "sampled to build the Length Weight Key (LWK), raw and SOP corrected fleet numbers,",
      "and mean weight at length per Year/Quarter (corrland =",
      paste(round(outputs$SOP_L$corrland, 3), collapse = ", "), ")"
    )
  ),
  options = list(pageLength = 30, autoWidth = TRUE),
  rownames = FALSE, filter = "top"
)
```


#### 3.3.2.2. Discards

```{r Numbers at length no weight Discards, echo=FALSE, warning=FALSE, message=FALSE, results='asis', eval = has_lengths[2]  & !has_LWK[2]}
# ---- SOP_L summary table ----
LF_summary_D <- outputs$LF %>% filter (SAcatchCat == "Dis"  ) %>% 
  dplyr::select(Quarter, FMclassMeasured,  number_raw_LFD, lenNumfleet) %>%
  mutate(
    lenNumfleet = round(lenNumfleet, 3),
  ) %>%
  rename(
    "Length" = FMclassMeasured,
    "Number_Raw_LFD" = number_raw_LFD,
    "Raised number (no SOP corr) (1000)" = lenNumfleet,
    "Quarter" = Quarter
  )

datatable(
  LF_summary_D,
  caption = htmltools::tags$caption(
    style = 'caption-side: top; text-align: left; color: black; font-weight: bold;',
    paste(
      "Table: Number of fish sampled for length frequency distribution (LFD), raw fleet numbers (no SOP correction) per Year/Quarter"
    )
  ),
  options = list(pageLength = 30, autoWidth = TRUE),
  rownames = FALSE, filter = "top"
)

```

```{r Numbers at length Discards, echo=FALSE, warning=FALSE, message=FALSE, results='asis', eval = has_LWK[2]}
# Function to generate tables for Landings and Discards
# ---- outputs$SOP_D summary table ----
LWK_summary_D <- outputs$SOP_D$MWAL %>%
  dplyr::select(Quarter, length, number_raw_LFD, number_raw_LWK, number, corr_numbers, indW2, CI_low, CI_high, indW2_var) %>%
    mutate(
    across(c(number, corr_numbers), ~ round(.x, 3)),
    across(c(indW2, CI_low, CI_high, indW2_var), ~ round(.x, 2))
  ) %>%
  rename(
    "Length" = length,
    "Number_Raw_LFD" = number_raw_LFD,
    "Number_Raw_LWK" = number_raw_LWK,
    "Number (1000)" = number,
    "Corrected_Number (1000)" = corr_numbers,
    "Individual_Weight (g)" = indW2,
    "Individual_Weight_CI_Low (g)" = CI_low,
    "Individual_Weight_CI_High (g)" = CI_high,
    "Individual_Variance (g^2)" = indW2_var,
    "Quarter" = Quarter
  )

datatable(
  LWK_summary_D,
  caption = htmltools::tags$caption(
    style = 'caption-side: top; text-align: left; color: black; font-weight: bold;',
    paste(
      "Table: Number of fish sampled for length frequency distribution (LFD),",
      "sampled to build the Length Weight Key (LWK), raw and SOP corrected fleet numbers,",
      "and mean weight at length per Year/Quarter (corrdis =",
      paste(round(outputs$SOP_D$corrdis, 3), collapse = ", "), ")"
    )
  ),
  options = list(pageLength = 30, autoWidth = TRUE),
  rownames = FALSE, filter = "top"
)
```

### 3.3.3. Numbers at length {.tabset}

```{r Number at length no SOP, echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=15, fig.height=10, eval = any(has_lengths) & !any(has_LWK)}
# Prepare annotation dataframe per Quarter (optional)
dev.off()
# Plot both Landings (Lan) and Discards (Dis)
p_LF <- ggplot(outputs$LF, aes(x = FMclassMeasured, y = lenNumfleet, color = SAcatchCat)) +
  geom_line(size = 1.2) +
  geom_point(shape = 21, size = 2, aes(fill = SAcatchCat)) +
  scale_color_manual(values = c("Lan" = "steelblue", "Dis" = "tomato")) +
  scale_fill_manual(values = c("Lan" = "steelblue", "Dis" = "tomato")) +
  scale_y_continuous(name = "Number (x1000)") +
  scale_x_continuous(name = "Length (cm)", breaks = unique(outputs$LF$FMclassMeasured)) +
  facet_wrap(~Quarter, scales = "free_y") +
  theme_bw(base_size = 14) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "bottom",
    legend.title = element_blank()
  )

p_LF

```

#### 3.3.3.1. Landings

```{r Numbers at length plots Landings, echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=fig_width_lan, fig.height=fig_height_lan, dpi=72, eval=has_LWK[1]}

library(ggpubr)

if (has_LWK[1] && !is.null(outputs$SOP_L)) {
    if ("MWAL" %in% names(outputs$SOP_L)) {
    df_L <- outputs$SOP_L$MWAL
    # get corrland seperately
    val_corrland <- outputs$SOP_L$corrland
  } else {
    # Quarter data
    q_names <- names(outputs$SOP_L)[grepl("^Q", names(outputs$SOP_L))]
    df_L <- bind_rows(lapply(q_names, function(q) {
      tmp <- outputs$SOP_L[[q]]$MWAL
      if(!is.null(tmp)) {
        tmp$Quarter <- q
        tmp$corr_factor <- outputs$SOP_L[[q]]$corrland
      }
      return(tmp)
    }))
    val_corrland <- df_L$corr_factor
  }

  df_L$length <- as.numeric(as.character(df_L$length))

  p_Lan <- plot_sop_general(df_L, val_corrland, "Landings - Numbers at length", 
                           mode = "number", ncol = ncol_val_lan)

  tmpfile <- tempfile(fileext = ".png")
  png(tmpfile, width = fig_width_lan*100, height = fig_height_lan*100, res = 150)
  
  # plot_sop_general geeft vaak een lijst met plots terug, ggarrange voegt ze samen
  if(is.list(p_Lan) && !inherits(p_Lan, "ggplot")) {
    print(ggpubr::ggarrange(plotlist = p_Lan, ncol = ncol_val_lan))
  } else {
    print(p_Lan)
  }
  
  dev.off()
  knitr::include_graphics(tmpfile)
}


#if (has_LWK[1] && !is.null(outputs$SOP_L)) {
 # df_L <- if ("MWAL" %in% names(outputs$SOP_L)) {
#    outputs$SOP_L$MWAL
 # } else {
  #  bind_rows(lapply(names(outputs$SOP_L)[grepl("^Q", names(outputs$SOP_L))], function(q) {
   #   tmp <- outputs$SOP_L[[q]]$MWAL
    #  tmp$Quarter <- q
     # tmp$corrland <- outputs$SOP_L[[q]]$corrland
      #tmp
  #  }))
  #}

#  p_Lan <- plot_sop_general(df_L, df_L$corrland, "Landings - Numbers at length", mode = "number", ncol= ncol_val_lan)
#  tmpfile <- tempfile(fileext = ".png")
 # png(tmpfile, width = fig_width_lan*100, height = fig_height_lan*100, res = 150)
  #print(do.call(ggarrange, c(p_Lan)))
  #dev.off()

  #knitr::include_graphics(tmpfile)
#}
```

#### 3.3.3.2. Discards

```{r Numbers at length plots Discards, echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=fig_width_dis, fig.height=fig_height_dis, dpi=72, eval=has_LWK[2]}
library(ggpubr)




if (has_LWK[2] && !is.null(outputs$SOP_D)) {
  
  if ("MWAL" %in% names(outputs$SOP_D)) {
    # YEAR DATA
    df_D <- outputs$SOP_D$MWAL
    val_corrdis <- outputs$SOP_D$corrdis
  } else {
    # Quarter data
    q_names <- names(outputs$SOP_D)[grepl("^Q", names(outputs$SOP_D))]
    df_D <- bind_rows(lapply(q_names, function(q) {
      tmp <- outputs$SOP_D[[q]]$MWAL
      if(!is.null(tmp)) {
        tmp$Quarter <- q
        # Sla de factor op in de tijdelijke df
        tmp$corr_factor <- outputs$SOP_D[[q]]$corrdis
      }
      return(tmp)
    }))
    val_corrdis <- df_D$corr_factor
  }

  df_D$length <- as.numeric(as.character(df_D$length))
  df_D$number <- as.numeric(as.character(df_D$number))
  df_D$corr_numbers <- as.numeric(as.character(df_D$corr_numbers))

  p_Dis <- plot_sop_general(
    df = df_D, 
    corr_values = val_corrdis, 
    title_prefix = "Discards - Numbers at length", 
    mode = "number", 
    ncol = ncol_val_dis
  )

  tmpfile <- tempfile(fileext = ".png")
  png(tmpfile, width = fig_width_dis*100, height = fig_height_dis*100, res = 150)
  
  if(is.list(p_Dis) && !inherits(p_Dis, "ggplot")) {
    print(ggpubr::ggarrange(plotlist = p_Dis, ncol = ncol_val_dis))
  } else {
    print(p_Dis)
  }
  
  dev.off()
  knitr::include_graphics(tmpfile)
}

#if (has_LWK[2] && !is.null(outputs$SOP_D)) {
#  df_D <- if ("MWAL" %in% names(outputs$SOP_D)) {
 #   outputs$SOP_D$MWAL
#  } else {
#    bind_rows(lapply(names(outputs$SOP_D)[grepl("^Q", names(outputs$SOP_D))], function(q) {
#      tmp <- outputs$SOP_D[[q]]$MWAL
#      tmp$Quarter <- q
#      tmp$corrdis <- outputs$SOP_D[[q]]$corrdis
#      tmp
#    }))
#  }

#  p_Dis <- plot_sop_general(df_D, df_D$corrdis, "Discards - Numbers at length", mode = "number", ncol= ncol_val_dis)

#  tmpfile <- tempfile(fileext = ".png")
 # png(tmpfile, width = fig_width_dis*100, height = fig_height_dis*100, res = 150)
  #print(do.call(ggarrange, c(p_Dis)))
  #dev.off()

#  knitr::include_graphics(tmpfile)
#}


```

### 3.3.4. Weight at length {.tabset}

#### 3.3.4.1. Landings 

```{r Mean weight at length Landings, echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=fig_width_lan, fig.height=fig_height_lan, eval=has_LWK[1]}
library(ggpubr)


if (has_LWK[1] && !is.null(outputs$SOP_L)) {

  if ("MWAL" %in% names(outputs$SOP_L)) {
    df_W_L <- outputs$SOP_L$MWAL
  } else {
    q_names <- names(outputs$SOP_L)[grepl("^Q", names(outputs$SOP_L))]
    df_W_L <- bind_rows(lapply(q_names, function(q) {
      tmp <- outputs$SOP_L[[q]]$MWAL
      if(!is.null(tmp)) tmp$Quarter <- q
      return(tmp)
    }))
  }

  df_W_L$length  <- as.numeric(as.character(df_W_L$length))
  df_W_L$indW2   <- as.numeric(as.character(df_W_L$indW2))
  df_W_L$CI_low  <- as.numeric(as.character(df_W_L$CI_low))
  df_W_L$CI_high <- as.numeric(as.character(df_W_L$CI_high))

  p_W_L <- plot_sop_general(
    df = df_W_L, 
    corr_values = NULL, 
    title_prefix = "Landings - Mean Weight at length", 
    mode = "weight", 
    ncol = ncol_val_lan
  )

  tmpfile <- tempfile(fileext = ".png")
  png(tmpfile, width = fig_width_lan*100, height = fig_height_lan*100, res = 150)
  
  if (is.list(p_W_L) && !inherits(p_W_L, "ggplot")) {
    print(ggpubr::ggarrange(plotlist = p_W_L, ncol = ncol_val_lan))
  } else {
    print(p_W_L)
  }
  
  dev.off()
  knitr::include_graphics(tmpfile)
}


#if (has_LWK[1] && !is.null(outputs$SOP_L)) {
#
 # p_W_L <- plot_sop_general(outputs$SOP_L$MWAL, NULL, "Landings - Mean Weight at length", mode = "weight", ncol= ncol_val_lan)

#  tmpfile <- tempfile(fileext = ".png")
#  png(tmpfile, width = fig_width_lan*100, height = fig_height_lan*100, res = 150)
#  print(do.call(ggarrange, c(p_W_L)))
#  dev.off()

#  knitr::include_graphics(tmpfile)
#}


```

#### 3.3.4.2. Discards 

```{r Mean weight at length Discards, echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=fig_width_dis, fig.height=fig_height_dis, eval=has_LWK[2]}
library(ggpubr)


if (has_LWK[2] && !is.null(outputs$SOP_D)) {

  if ("MWAL" %in% names(outputs$SOP_D)) {
    df_W_D <- outputs$SOP_D$MWAL
  } else {
    q_names <- names(outputs$SOP_D)[grepl("^Q", names(outputs$SOP_D))]
    df_W_D <- bind_rows(lapply(q_names, function(q) {
      tmp <- outputs$SOP_D[[q]]$MWAL
      if(!is.null(tmp)) tmp$Quarter <- q
      return(tmp)
    }))
  }

  df_W_D$length  <- as.numeric(as.character(df_W_D$length))
  df_W_D$indW2   <- as.numeric(as.character(df_W_D$indW2))
  df_W_D$CI_low  <- as.numeric(as.character(df_W_D$CI_low))
  df_W_D$CI_high <- as.numeric(as.character(df_W_D$CI_high))

  p_W_D <- plot_sop_general(
    df = df_W_D, 
    corr_values = NULL, 
    title_prefix = "Discards - Mean Weight at length", 
    mode = "weight", 
    ncol = ncol_val_dis
  )

  tmpfile <- tempfile(fileext = ".png")
  png(tmpfile, width = fig_width_dis*100, height = fig_height_dis*100, res = 150)
  
  if (is.list(p_W_D) && !inherits(p_W_D, "ggplot")) {
    print(ggpubr::ggarrange(plotlist = p_W_D, ncol = ncol_val_dis))
  } else {
    print(p_W_D)
  }
  
  dev.off()
  knitr::include_graphics(tmpfile)
}

#if (has_LWK[1] && !is.null(outputs$SOP_D)) {

#  p_W_D <- plot_sop_general(outputs$SOP_D$MWAL, NULL, "Discards - Mean Weight at length", mode = "weight", ncol= ncol_val_dis)

 # tmpfile <- tempfile(fileext = ".png")
  #png(tmpfile, width = fig_width_dis*100, height = fig_height_dis*100, res = 150)
  #print(do.call(ggarrange, c(p_W_D)))
  #dev.off()

  #knitr::include_graphics(tmpfile)
#}


```


## 3.4. Raised numbers at age and mean weight at age {.tabset}

### 3.4.1 domainBiology in catch and length distribution tables (CN and DN)

```{r domainBiology_age, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
library(dplyr)
library(DT)

# Extract unique domainBiology from catch
domain_catch <- tables$catch %>%
  dplyr::filter(domainBiology != "") %>%
  dplyr::distinct(domainBiology, catchCategory, seasonValue, metier6) %>%
  dplyr::mutate(in_catch = TRUE)

# Extract distribution presence per variableType, then pivot wide
domain_dist <- tables$distribution %>%
  dplyr::filter(domainBiology != "") %>%
  dplyr::filter(distributionType == "Age") %>%
  dplyr::distinct(domainBiology, catchCategory, variableType) %>%
  dplyr::mutate(present = TRUE) %>%
  tidyr::pivot_wider(
    names_from  = variableType,
    values_from = present,
    names_prefix = "in_distribution_",
    values_fill  = FALSE
  )

# Join
domain_summary <- domain_catch %>%
  dplyr::full_join(domain_dist, by = c("domainBiology", "catchCategory")) %>%
  dplyr::mutate(
    in_catch = tidyr::replace_na(in_catch, FALSE),
    # Replace NA with FALSE for all in_distribution_* columns
    dplyr::across(dplyr::starts_with("in_distribution_"), ~ tidyr::replace_na(.x, FALSE))
  ) %>%
  # Overall status: OK only if catch present AND all distribution types present
  dplyr::mutate(
    status = dplyr::case_when(
      !in_catch                                          ~ "⚠️ Missing in catch",
      in_catch & dplyr::if_all(
        dplyr::starts_with("in_distribution_"), ~ .x)   ~ "OK",
      in_catch & dplyr::if_any(
        dplyr::starts_with("in_distribution_"), ~ .x)   ~ "⚠️ Partially missing in distribution",
      in_catch                                           ~ "⚠️ Missing in distribution",
      TRUE                                               ~ "Unknown"
    )
  ) %>%
  dplyr::arrange(status, domainBiology)

# Render
datatable(
  domain_summary,
  caption  = paste0("Summary of domainBiology in catch and distribution table (CN) for age - ", istock),
  options  = list(pageLength = 30, autoWidth = TRUE),
  rownames = FALSE
) %>%
  DT::formatStyle(
    "status",
    backgroundColor = DT::styleEqual(
      c("OK",
        "⚠️ Partially missing in distribution",
        "⚠️ Missing in distribution",
        "⚠️ Missing in catch"),
      c("#d4edda", "#fff3cd", "#f8d7da", "#f8d7da")
    )
  ) %>%
  # Highlight individual in_distribution_* columns: green TRUE, red FALSE
  DT::formatStyle(
    columns = names(domain_summary)[startsWith(names(domain_summary), "in_distribution_")],
    backgroundColor = DT::styleEqual(c(TRUE, FALSE), c("#d4edda", "#f8d7da"))
  )
```

### 3.4.2. Summary table at age {.tabset}

#### 3.4.2.1. Landings

```{r Numbers at age Landings, echo=FALSE, warning=FALSE, message=FALSE, results='asis', eval = has_ALK[1]}
# Function to generate tables for Landings and Discards
# SOP_L summary table
library(dplyr)
library(DT)
library(htmltools)

# ---- SOP_L summary table ----
ALK_summary_L <- outputs$LNAA %>%
  dplyr::select(Quarter, Age, number_raw, SopCorrNAA, MWAA,CI_low, CI_high, MWAA_var) %>%
  mutate(
    # Round corrected number to 3 decimals
    SopCorrNAA = round(SopCorrNAA, 3),
    # Round all weight-related variables to 2 decimals
    across(c(MWAA, CI_low, CI_high, MWAA_var), ~ round(.x, 2))
  ) %>%
  rename(
    "Age" = Age,
    "Number_Raw_ALK" = number_raw,
    "Corrected_Number (1000)" = SopCorrNAA,
    "Individual_Weight (g)" = MWAA,
    "Individual_Weight_CI_Low (g)" = CI_low,
    "Individual_Weight_CI_High (g)" = CI_high,
    "Individual_Weight_Variance (g^2)" = MWAA_var,
    "Quarter" = Quarter
  )

datatable(
  ALK_summary_L,
  caption = htmltools::tags$caption(
    style = 'caption-side: top; text-align: left; color: black; font-weight: bold;',
    paste(
      "Table: Number of fish sampled to build the Age Length Key (ALK),",
      "SOP corrected fleet numbers,",
      "and mean weight at age per Year/Quarter"   )
  ),
  options = list(pageLength = 30, autoWidth = TRUE),
  rownames = FALSE, filter = "top"
)
```

#### 3.4.2.2. Discards

```{r Numbers at age Discards, echo=FALSE, warning=FALSE, message=FALSE, results='asis', eval = has_ALK[2]}
# ---- SOP_L summary table ----
ALK_summary_D <- outputs$DNAA %>%
  dplyr::select(Quarter, Age, number_raw, SopCorrNAA, MWAA, CI_low, CI_high, MWAA_var) %>%
  mutate(
    # Round corrected number to 3 decimals
    SopCorrNAA = round(SopCorrNAA, 3),
    # Round all weight-related variables to 2 decimals
    across(c(MWAA, CI_low, CI_high, MWAA_var), ~ round(.x, 2))
  ) %>%
  rename(
    "Age" = Age,
    "Number_Raw_ALK" = number_raw,
    "Corrected_Number (1000)" = SopCorrNAA,
    "Individual_Weight (g)" = MWAA,
    "Individual_Weight_CI_Low (g)" = CI_low,
    "Individual_Weight_CI_High (g)" = CI_high,
    "Individual_Weight_Variance (g^2)" = MWAA_var,
    "Quarter" = Quarter
  )


datatable(
  ALK_summary_D,
  caption = htmltools::tags$caption(
    style = 'caption-side: top; text-align: left; color: black; font-weight: bold;',
    paste(
      "Table: Number of fish sampled to build the Age Length Key (ALK),",
      "SOP corrected fleet numbers,",
      "and mean weight at age per Year/Quarter"   )
  ),
  options = list(pageLength = 30, autoWidth = TRUE),
  rownames = FALSE, filter = "top"
)
```

### 3.4.3. ALK plots {.tabset}

#### 3.4.3.1. Landings

```{r ALK Landings, echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=fig_width_lan, fig.height=fig_height_lan, eval=has_ALK[1]}

plots_list <- list()


# --- Landings ---
if (has_ALK[1] && !is.null(outputs$ALK_LAN)) {
  
  if (toupper(meta$iYQ$Lan) == "YEAR") {
    raw_plots_LAN <- outputs$ALK_LAN$plot$raw()
    model_plots_LAN <- outputs$ALK_LAN$plot$model()
  } else {
    quarters_LAN <- names(outputs$ALK_LAN)
    raw_plots_LAN <- lapply(quarters_LAN, function(q) outputs$ALK_LAN[[q]]$plot$raw())
    model_plots_LAN <- lapply(quarters_LAN, function(q) outputs$ALK_LAN[[q]]$plot$model())
  }
  
  plots_list[["Lan_raw"]] <- raw_plots_LAN
  plots_list[["Lan_model"]] <- model_plots_LAN
}

```

#### 3.4.3.2. Discards

```{r ALK Discards, echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=fig_width_dis, fig.height=fig_height_dis, eval=has_ALK[2]}

if (has_ALK[2] && !is.null(outputs$ALK_DIS)) {
  
  if (toupper(meta$iYQ$Dis) == "YEAR") {
    raw_plots_DIS <- outputs$ALK_DIS$plot$raw()
    model_plots_DIS <- outputs$ALK_DIS$plot$model()
  } else {
    quarters_DIS <- names(outputs$ALK_DIS)
    raw_plots_DIS <- lapply(quarters_DIS, function(q) outputs$ALK_DIS[[q]]$plot$raw())
    model_plots_DIS <- lapply(quarters_DIS, function(q) outputs$ALK_DIS[[q]]$plot$model())
  }
  
  plots_list[["Dis_raw"]] <- raw_plots_DIS
  plots_list[["Dis_model"]] <- model_plots_DIS
}

```

### 3.4.4. Numbers at age {.tabset}

#### 3.4.4.1. Landings

```{r Numbers at age plots Landings, echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=fig_width_lan, fig.height=fig_height_lan, eval=has_ALK[1]}

library(ggpubr)


if (has_ALK[1] && !is.null(outputs$LNAA)) {

  df_LNAA <- outputs$LNAA
  
  if (is.data.frame(df_LNAA)) {
    # FIX: dwing Age en number naar numeriek om as-fouten te voorkomen
    if("age" %in% names(df_LNAA)) df_LNAA$age <- as.numeric(as.character(df_LNAA$age))
    if("number" %in% names(df_LNAA)) df_LNAA$number <- as.numeric(as.character(df_LNAA$number))
    
    # Zorg dat Quarter bestaat voor de plotfunctie
    if(!"Quarter" %in% names(df_LNAA)) df_LNAA$Quarter <- "YEAR"
  }

  p_L_number <- plot_alk(
    df = df_LNAA, 
    mode = "number", 
    title_prefix = "Landings - Numbers at Age", 
    ncol = ncol_val_lan
  )

  tmpfile <- tempfile(fileext = ".png")
  png(tmpfile, width = fig_width_lan*100, height = fig_height_lan*100, res = 150)
  
  if (is.list(p_L_number) && !inherits(p_L_number, "ggplot")) {
    print(ggpubr::ggarrange(plotlist = p_L_number, ncol = ncol_val_lan))
  } else {
    print(p_L_number)
  }
  
  dev.off()
  knitr::include_graphics(tmpfile)
}


#if (has_ALK[1] && !is.null(outputs$LNAA)) {

#  p_L_number <- plot_alk(outputs$LNAA, mode = "number", title_prefix = "Discards - Numbers at Age", ncol=ncol_val_lan) 

#  tmpfile <- tempfile(fileext = ".png")
#  png(tmpfile, width = fig_width_lan*100, height = fig_height_lan*100, res = 150)
#  print(do.call(ggarrange, c(p_L_number)))
#  dev.off()

#  knitr::include_graphics(tmpfile)
#}

```

#### 3.4.4.2. Discards

```{r Numbers at age plots Discards, echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=fig_width_dis, fig.height=fig_height_dis, eval=has_ALK[2]}
library(ggpubr)



if (has_ALK[2] && !is.null(outputs$DNAA)) {

  # 1. Data voorbereiden
  df_DNAA <- outputs$DNAA
  
  if (is.data.frame(df_DNAA)) {
    if("age" %in% names(df_DNAA)) df_DNAA$age <- as.numeric(as.character(df_DNAA$age))
    if("number" %in% names(df_DNAA)) df_DNAA$number <- as.numeric(as.character(df_DNAA$number))
    
    if(!"Quarter" %in% names(df_DNAA)) df_DNAA$Quarter <- "YEAR"
  }

  p_D_number <- plot_alk(
    df = df_DNAA, 
    mode = "number", 
    title_prefix = "Discards - Numbers at Age", 
    ncol = ncol_val_dis
  )

  if (!is.null(p_D_number)) {
    
    tmpfile <- tempfile(fileext = ".png")
    png(tmpfile, width = fig_width_dis*100, height = fig_height_dis*100, res = 150)
    
    if (is.list(p_D_number) && !inherits(p_D_number, "ggplot")) {
      # Bij kwartaaldata (lijst van plots)
      print(ggpubr::ggarrange(plotlist = p_D_number, ncol = ncol_val_dis))
    } else {
      # Bij jaardata (enkele ggplot)
      print(p_D_number)
    }
    
    dev.off()
    knitr::include_graphics(tmpfile)
    
  } else {
    message("No Numbers at Age plots for Discards")
  }
}

#if (has_ALK[2] && !is.null(outputs$DNAA)) {

#  p_D_number <- plot_alk(outputs$DNAA, mode = "number", title_prefix = "Discards - Numbers at Age", ncol=ncol_val_dis)

 # if (!is.null(p_D_number) && length(p_D_number) > 0) {

  #  p_D_number <- unlist(p_D_number, recursive = TRUE)

   # tmpfile <- tempfile(fileext = ".png")
    #png(tmpfile, width = fig_width_lan*100, height = fig_height_lan*100, res = 150)
    #print(do.call(ggarrange, c(p_D_number)))
    #dev.off()

    #knitr::include_graphics(tmpfile)
#  } else {
 #   message("No Numbers at Age plots for Discards")
  #}
#}


```

### 3.4.5. Weight at age {.tabset}

#### 3.4.5.1. Landings

```{r Mean weight at age Landings, echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=fig_width_lan, fig.height=fig_height_lan, eval=has_ALK[1]}
library(ggpubr)


if (has_ALK[1] && !is.null(outputs$LNAA)) { # Let op: Meestal is LNAA index [1]

  df_LNAA_W <- outputs$LNAA
  
  if (is.data.frame(df_LNAA_W)) {
    df_LNAA_W$age     <- as.numeric(as.character(df_LNAA_W$Age))
    df_LNAA_W$indW2   <- as.numeric(as.character(df_LNAA_W$MWAA))
    df_LNAA_W$CI_low  <- as.numeric(as.character(df_LNAA_W$CI_low))
    df_LNAA_W$CI_high <- as.numeric(as.character(df_LNAA_W$CI_high))
    
    if(!"Quarter" %in% names(df_LNAA_W)) df_LNAA_W$Quarter <- "YEAR"
  }

  p_L_weight <- plot_alk(
    df = df_LNAA_W, 
    mode = "weight", 
    title_prefix = "Landings - Mean Weight at Age", 
    ncol = ncol_val_lan
  )

  if (!is.null(p_L_weight)) {
    
    tmpfile <- tempfile(fileext = ".png")
    png(tmpfile, width = fig_width_lan*100, height = fig_height_lan*100, res = 150)
    
    # 4. Veilige PRINT-check (GEEN unlist gebruiken!)
    if (is.list(p_L_weight) && !inherits(p_L_weight, "ggplot")) {
      # Geval: Kwartaaldata (Lijst van plots)
      print(ggpubr::ggarrange(plotlist = p_L_weight, ncol = ncol_val_lan))
    } else {
      # Geval: Jaardata (Enkele ggplot)
      print(p_L_weight)
    }
    
    dev.off()
    knitr::include_graphics(tmpfile)
    
  } else {
    message("No Weight at Age plots for Landings")
  }
}


# 
# if (has_ALK[2] && !is.null(outputs$LNAA)) {
# 
#   p_L_weight <- plot_alk(outputs$LNAA, mode = "weight", title_prefix = "Landings - Mean Weight at Age", ncol=ncol_val_lan)
# 
#   if (!is.null(p_L_weight) && length(p_L_weight) > 0) {
# 
#     p_L_weight <- unlist(p_L_weight, recursive = TRUE)
# 
#     tmpfile <- tempfile(fileext = ".png")
#     png(tmpfile, width = fig_width_lan*100, height = fig_height_lan*100, res = 150)
#     print(do.call(ggarrange, c(p_L_weight)))
#     dev.off()
# 
#     knitr::include_graphics(tmpfile)
#   } else {
#     message("No Weight at Age plotds for Landings")
#   }
# }

```

#### 3.4.5.2. Discards

```{r Mean weight at age Discards, echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=fig_width_dis, fig.height=fig_height_dis, eval=has_ALK[2]}
library(ggpubr)

if (has_ALK[2] && !is.null(outputs$DNAA)) {

  df_DNAA_W <- outputs$DNAA
  
  if (is.data.frame(df_DNAA_W)) {
    df_DNAA_W$age     <- as.numeric(as.character(df_DNAA_W$Age))
    df_DNAA_W$indW2   <- as.numeric(as.character(df_DNAA_W$MWAA))
    df_DNAA_W$CI_low  <- as.numeric(as.character(df_DNAA_W$CI_low))
    df_DNAA_W$CI_high <- as.numeric(as.character(df_DNAA_W$CI_high))
    
    if(!"Quarter" %in% names(df_DNAA_W)) df_DNAA_W$Quarter <- "YEAR"
  }

  p_D_weight <- plot_alk(
    df = df_DNAA_W, 
    mode = "weight", 
    title_prefix = "Discards - Mean Weight at Age", 
    ncol = ncol_val_dis
  )

  if (!is.null(p_D_weight)) {
    
    tmpfile <- tempfile(fileext = ".png")
    png(tmpfile, width = fig_width_dis*100, height = fig_height_dis*100, res = 150)
    
    # 4. Veilige PRINT-check (Verwijder unlist!)
    if (is.list(p_D_weight) && !inherits(p_D_weight, "ggplot")) {
      # Kwartaaldata (Lijst van plots)
      print(ggpubr::ggarrange(plotlist = p_D_weight, ncol = ncol_val_dis))
    } else {
      # Jaardata (Enkele ggplot)
      print(p_D_weight)
    }
    
    dev.off()
    knitr::include_graphics(tmpfile)
    
  } else {
    message("No Weight at Age plots for Discards")
  }
}




# if (has_ALK[2] && !is.null(outputs$DNAA)) {
# 
#   p_D_weight <- plot_alk(outputs$DNAA, mode = "weight", title_prefix = "Discards - Mean Weight at Age", ncol=ncol_val_dis)
# 
#   if (!is.null(p_D_weight) && length(p_D_weight) > 0) {
# 
#     p_D_weight <- unlist(p_D_weight, recursive = TRUE)
# 
#     tmpfile <- tempfile(fileext = ".png")
#     png(tmpfile, width = fig_width_dis*100, height = fig_height_dis*100, res = 150)
#     print(do.call(ggarrange, c(p_D_weight)))
#     dev.off()
# 
#     knitr::include_graphics(tmpfile)
#   } else {
#     message("No Weight at Age plots for Discards")
#   }
# }

```
